### 2025-11-18 CV3/awards.tex
-

\section{Honors and Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)

	\item \textbf{Russian President’s Scholarship for High School Sudents}, given for prize-winning at final round of All-Russian School Olympiads, 2012-2014
	\item \textbf{Moscow Governor’s Scholarship for High School Sudents}, given for prize-winning at region and final rounds of All-Russian School Olympiads, 2012-2014

	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg, 2014
	\item \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow, 2014
	\item \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow, 2014

	\item \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok, 2013
	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk, 2012
\end{enumerate}
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

>>>>

\section{Награды}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
  \item \href{https://ai-awards.ru/}{\textbf{Национальная премия ``Лидеры ИИ'' 2025}}, Конференция ``AI Journey''
  \item \href{https://media.innopolis.university/news/yandex-research-employee-receives-polyak-prize/}{\textbf{Премия имени Б.Т. Поляка для молодых учёных 2025}}, Университет Иннополиc
  \item  \textbf{Студенческая премия за отличные успехи в науке}, Научно-технологический университет имени короля Абдаллы, 2021
  \item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Лучшая студенческая работа воркшопа FL-ICML 2021}}
  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Научная премия Яндекса 2021}}, Яндекс
    %   \item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Научная премия Яндекса 2020}}, Яндекс
    %   \item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
  \item \textbf{Стипендия Абрамова за отличные успехи в учебе}, Московский физико-технический институт, 2015-2017
  \item \textbf{Азиатская физическая олимпиада (APhO) 2014, похвальная грамота}, Сингапур

  \item \textbf{Russian President’s Scholarship for High School Sudents}, given for prize-winning at final round of All-Russian School Olympiads, 2012-2014
    %   \item \textbf{Moscow Governor’s Scholarship for High School Sudents}, given for prize-winning at region and final rounds of All-Russian School Olympiads, 2012-2014

  \item \textbf{Призер заключительного этапа Всеросийской олимпиады школьников по физике}, Санкт-Петербург, 2014

  \item \textbf{Победитель регионального этапа Всеросийской олимпиады школьников по информатике}, Москва, 2014
  \item \textbf{Победитель регионального этапа Всеросийской олимпиады школьников по математике}, Москва, 2014
  \item \textbf{Победитель заключительного этапа Всеросийской олимпиады школьников по физике}, Владивосток, 2013
  \item \textbf{Призер заключительного этапа Всеросийской олимпиады школьников по физике}, Саранск, 2012
\end{enumerate}
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

### 2025-11-18 CV3/general.tex
-

\section{Опыт работы}
\begin{tabular}{rl}
  \textsc{2023-н.в.}& Ведущий исследователь\\
  &\textbf{\href{https://research.yandex.com}{\color{black}Яндекс}}, Москва, Россия\\
  \textsc{2022-2023}& Постдокторантура\\
  & \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Католический университет Лувена}}, Лувен-ла-Нёв, Бельгия\\
  \textsc{2021-2023}& Стажер-исследователь\\
  &Исследовательский центр доверенного искусственного интеллекта\\
  &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
  \\&Москва, Россия\\
  \textsc{2022}& Исследователь\\
  &Лаборатория продвинутой комбинаторики и сетевых приложений\\
  &\textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия
\end{tabular}

@@

\section{Education}
\begin{tabular}{rl}
  \textsc{2019-2022}& PhD in Computer Science\\
  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
  & Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
  & Thesis: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
  & \hspace{\widthof{Thesis: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
  & Defense Committee: -- External: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Yurii Nesterov}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Arkadi Nemirovsky}\\
  &\hspace{\widthof{Defense Committee: }}-- Internal: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E. Keyes}, \href{https://shao3wangdi.github.io}{Di Wang}, \href{https://scholar.google.com/citations?user=Vj2D8JQAAAAJ}{Matteo Parsani}\\
  \textsc{2018-2021}& MS in Applied Mathematics and Physics\\
  & \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
  & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
  \textsc{2018-2019}& MS in Computer Science\\
  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
  & Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
  \textsc{2014-2018}& BS in Applied Mathematics and Physics\\
  & \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
  & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\end{tabular}

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
  &  Optimization, Federated and Distributed Learning\\
  &Machine Learning, Deep Learning
\end{tabular}

>>>>

\section{Опыт работы}
\begin{tabular}{rl}
  \textsc{2023-н.в.}& Ведущий исследователь\\
  &\textbf{\href{https://research.yandex.com}{\color{black}Яндекс}}, Москва, Россия\\
  \textsc{2022-2023}& Постдокторантура\\
  & \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Католический университет Лувена}}, Лувен-ла-Нёв, Бельгия\\
  \textsc{2021-2023}& Стажер-исследователь\\
  &Исследовательский центр доверенного искусственного интеллекта\\
  &\textbf{\href{https://www.ispras.ru/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
  Москва, Россия\\
  \textsc{2022}& Исследователь\\
  &Лаборатория продвинутой комбинаторики и сетевых приложений\\
  &\textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия
\end{tabular}

@@

\section{Образование}
\begin{tabular}{rl}
  \textsc{2019-2022}& Доктор философии (PhD) по компьютерным наукам\\
  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}Научно-технологический университет имени короля Абдаллы}}, Тувал, Саудовская Аравия\\
  & Руководитель: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
  & Диссертация: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
  & \hspace{\widthof{Диссертация: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
  & Диссертационный совет: -- Внешний: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Юрий Нестеров}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Аркадий Немировский}\\
  &\hspace{\widthof{Диссертационный совет: }}-- Внутренний: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E. Keyes}, \href{https://shao3wangdi.github.io}{Di Wang}, \href{https://scholar.google.com/citations?user=Vj2D8JQAAAAJ}{Matteo Parsani}\\
  \textsc{2018-2021}& Магистр прикладных математики и физики\\
  & \textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия\\
  & Руководитель: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Александр Гасников}\\
  \textsc{2018-2019}& Магистр компьютерных наук\\
  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}Научно-технологический университет имени короля Абдаллы}}, Тувал, Саудовская Аравия\\
  & Руководитель: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
  \textsc{2014-2018}& Бакалавр прикладных математики и физики\\
  & \textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия\\
  & Руководитель: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Александр Гасников}\\
\end{tabular}

\section{Научные интересы}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
  &  Оптимизация, Федеративное и распределенное обучение\\
  & Машинное обучение, Глубокое обучение
\end{tabular}

### 2025-11-18 CV3/papers.tex
-

\section{Publications}

@@

\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2024/hash/af10f27d0a48175e486a647c06c7a9c6-Abstract-Conference.html}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{Advances in Neural Information Processing Systems}, 2024.

@@

\textbf{\href{https://link.springer.com/rwe/10.1007/978-3-030-54621-2_860-1}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov). \textit{International Conference on Optimization and Applications}, 2021.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin). \textit{International Conference on Optimization and Applications}, 2021.

@@

\textbf{\href{https://crm-en.ics.org.ru/journal/article/references/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev). \textit{Computer research and modeling}, 2018.

@@

\section{Preprints}

@@

\textbf{\href{https://arxiv.org/abs/2507.09823}{Nesterov Finds GRAAL: Optimal and Adaptive Gradient Method for Convex Optimization}} (Ekaterina Borodich, Dmitry Kovalev). \textit{arXiv preprint arXiv:2507.09823}, 2025.

>>>>

\section{Публикации}

@@

    \textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{Advances in Neural Information Processing Systems}, 2024.

@@

    \textbf{\href{https://link.springer.com/content/pdf/10.1007/978-3-030-54621-2_860-1.pdf}{Decentralized Convex Optimization over Time-Varying Graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

    \textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov). \textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.

@@

    \textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin). \textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.

@@

    \textbf{\href{http://crm-en.ics.org.ru/journal/article/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev). \textit{Computer research and modeling}, 2018.

@@

\section{Препринты}

@@
